\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{authblk}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{url}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

% paper title
\title{Badass Title}

% author names and affiliations
\author[1]{Micah Keith Harlan}
\author[1]{Jianger Yu}
\author[1]{Baiyi Zhang}

% For affiliations, directly adjust the font size using \small, \footnotesize, etc.
\affil[1]{{\small \{mharlan25, jianger, baiyi\}@vt.edu}}
\affil[1]{{\small Department of Computer Science, Virginia Polytechnic Institute and State University, Falls Church, VA, USA}}

% make the title area
\maketitle

% abstract
\begin{abstract}
The rise of streaming services has revolutionized the way we consume media, offering an unprecedented volume of content at our fingertips. However, this abundance has led to a paradox of choice, where users often find themselves overwhelmed, scrolling through streaming platforms for extended periods without being able to decide on a movie to watch. Traditional search mechanisms in these platforms typically hinge on metadata such as movie titles, genres, and actor names, which, despite their utility, often need to catch up in catering to the nuanced preferences of users. By incorporating Large Language Models (LLMs), it can offer a more nuanced search capability, allowing users to find movies based on detailed aspects of the content, such as thematic elements, narrative style, or emotional tone, far beyond what conventional metadata can provide. This paper aims to provide an innovative way in regards to query and recommend movies to users, by providing an interactive application, where a user can query for, and get recommended movies to reduce user browsing time.
\end{abstract}

% Note that keywords are not normally used for peer-review papers.
\begin{IEEEkeywords}
IEEE, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

\section{Introduction}
% The very first letter is a 2-line initial drop letter followed by the rest of the first word in caps.
\IEEEPARstar{M}{ovie} streaming services have revolutionized the way we consume entertainment, offering users the power of choice and flexibility. Users can watch virtually anything they want anytime they want. Streaming services have provided many advantages for the user, but with these advantages come challenges. Users have been faced with an overabundance of movies and or content to choose from. Streaming services provide users with a plethora of options, but users often find themselves scrolling for long periods, without selecting content to watch. The challenge underscores the urgent need for a movie data search and recommendation system capable of providing information to the user’s query as well as providing better suggestions to both the query and individual user preferences. 
\newline
\indent
This project aims to build an innovative movie information retrieval (IR) and recommendation system. The main function is to respond to users’ queries by (1) searching specific information such as the title and cast of the movie or (2) providing generic movie recommendations using machine learning. The main tasks of the project includes retrieving data from both indexed databases and the Internet, providing Top-N movie recommendations for the search using ranking algorithms, and displaying the search results in a User Interface (UI). To ensure both usability and performance, the project will also involve pre-training the machine learning model for recommendation and utilizing large language models (LLMs) for enhancing query rewriting and summarizing search results, in addition to the primary tasks.\cite{manning2008introduction}.

\section{Conclusion}
The conclusion goes here.

% references section
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, proposal-ref}

\end{document}